INSTRUCTIONS TO PREPARE A FULL PAPER FOR THE 9th EUROPEAN CONGRESS ON COMPUTATIONAL METHODS IN APPLIED SCIENCES AND ENGINEERING\break ECCOMAS CONGRESS 2024

### 2024-02-27 paper/paper.tex
paper: add loc rom error plot

\subsection{Projection Error}
The projection error is computed for a test set for each configuration that was computed
using the FOM. Each test set has size $n_{test}$.

@@

>>>>

\subsubsection{Projection Error}
The projection error is computed for a test set for each configuration that was computed
using the FOM. Each test set has size $n_{test}$.

@@

\subsection{Localized ROM}

\begin{figure}[!htb]
    \includegraphics[width=\linewidth]{../work/beam/fig_loc_rom_error.pdf}
    \caption{A really Awesome Image}\label{fig:loc_rom_error}
\end{figure}
